---
title: "Jenny and Eric Spending Report, February"
output:
  pdf_document:
    toc: true
    toc_depth: 5
date: "2026-01-29"
---

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning =  FALSE, message = FALSE)
```

```{r}
library(XML)
library(RCurl)
library(rlist)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(readr)
library(sf)
unloadNamespace("EHData")
devtools::install_github("ericonsi/EHData")
library(EHData)
library(devtools)
library(roxygen2)
library(Hmisc)
library(psych)
library(tidyverse)
library(skimr)
library(purrr)
library(tidyr)
library(tidyverse)
library(gridExtra)
library(lubridate)
library(fastDummies)
library(data.table)
library(mltools)
library(MASS)
library(car)
library(patchwork)
library(ggthemes)
library(tinytex)
library(stats)
library(ggsci)
library(scales)
library(naniar)
library(caret)
library(pROC)
library(methods) 
library(sf)
library(mapproj)
library(maps)
#library(rnaturalearth)
library(rnaturalearthdata)
library(usmap)
library(tsibbledata)
library(tsibble)
library(forecast)
library(fpp3)
library(fable)
library(lme4)
library(rvest)
library(factoextra)
library(gridGraphics)
library(kableExtra)
library(anytime)
unloadNamespace("EHDataFinances")
devtools::install_github("ericonsi/EHDataFinances")
library(EHDataFinances)
library(knitr)
library(datefixR)
```

```{r}
#Assign Month

xMonth="2603"
Folder = xMonth
EH_Turquoise = "#33a0a0"
EH_Cream = "#FFFEE0"
EH_Squash = "#c95b0c"
EH_LabelColor = "#5d3f6a"

```

```{r}

# Import data

dfExpenses <- EHFinances_ImportRawAccountFiles(xMonth)[[1]]
dfCategories <- EHFinances_ImportCategories()
dfAmazonOrders <- EHFinances_ImportAmazonOrders(xMonth)
dfExpenses2025 <- EHFinances_Import2025()

```

```{r}
# Assign Categories and Shocks

dfExpenses2 <- EHFinances_AssignCategoriesAndSubcategories(dfExpenses)
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2025-12-28", "2026-01-08", "Rio")
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2026-02-2", "2026-02-10", "Puerto Rico")
dfExpenses4 <- EHFinances_AssignRuby(dfExpenses3)
dfExpenses5 <- EHFinances_AssignAccountsToDelete(dfExpenses4)
dfExpenses6 <- EHFinances_ApplyBusinessRules(dfExpenses5)
dfExpenses7 <- EHFinances_AssignFoodSubCategories(dfExpenses6)
dfExpenses8 <- EHFinances_AssignShoppingCategories(dfExpenses7)

```

```{r}

#Write or open override file

dfExpenses9 <- EHFinances_WriteOrOpenOverrideFile(dfExpenses8, Folder=xMonth, AlreadyWritten = TRUE)

```

```{r}
# Disaggregate Files - only works after override file has been written

liExpenseDFs <- EHFinances_CreateShockAndExpenseDFs(dfExpenses9)

dfExpensesReviewed = liExpenseDFs[[1]]
dfRuby <- liExpenseDFs[[2]]
dfRenovation <- liExpenseDFs[[3]]
dfIncomeTaxes <- liExpenseDFs[[4]]

```

```{r}

#Create/retrieve df for shopping analysis

dfShopping <- EHFinances_WriteOrOpenShoppingFile(dfExpensesReviewed, Folder=xMonth, AlreadyWritten = TRUE)

```

```{r}
# Create ytd dfs
# Needs an Override_r file


liExpenseDFs <- EHFinances_CreateYtdDfs(Folder)

dfExpensesReviewed_YTD = liExpenseDFs[[1]][[1]]
dfRuby_YTD <- liExpenseDFs[[1]][[2]]
dfRenovation_YTD <- liExpenseDFs[[1]][[3]]
dfIncomeTaxes_YTD <- liExpenseDFs[[1]][[4]]
dfShopping_YTD <- liExpenseDFs[[2]][[1]]

```

```{r}
#Perform Budget Analysis

liBudget <- EHFinances_CreateBudgetAnalysisDFs(dfExpensesReviewed, dfExpensesReviewed_YTD, Folder)

dfBudget <- liBudget[[1]]
dfBudget_YTD <- liBudget[[2]]

```

## 1. Overall Spending

```{r fig.width = 14, fig.height=8}

EHFinances_CreateTotalsTable(dfExpensesReviewed, dfExpensesReviewed_YTD, dfRuby, dfRuby_YTD, dfRenovation, dfRenovation_YTD, dfIncomeTaxes, dfIncomeTaxes_YTD, dfBudget, dfBudget_YTD, Folder)

```

### a. Spending by Category

```{r fig.width = 14, fig.height=8}

a <- EHData::EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |> dplyr::select(Category, Amount), xfill =EH_Turquoise, rectfill = EH_Cream, font_size = 15, xtitle = "Total Spent by Category, 2602", labelColor=EH_LabelColor, labelSize = 5)

b <- EHData::EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |> dplyr::select(Category, Amount), xfill =EH_Turquoise, rectfill = EH_Cream, font_size = 15, xtitle = "Total Spent by Category, YTD", labelColor=EH_LabelColor, labelSize = 5)

par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
grid.arrange(a, b, ncol = 2)

```

### b. Spending Compared to Budget (Goal: $173,000/Year, 14,440 per month)

```{r}
#par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
grid.arrange(liBudget[[3]], liBudget[[4]], ncol = 2)

kable(dfBudget,  caption = "Budget Summary", format.args = list(big.mark = ","), digits = 0) |>
    kable_styling(full_width = FALSE, position = "center",
                  latex_options = c("striped", "hold_position"))

kable(dfBudget_YTD,  caption = "Budget Summary YTD", format.args = list(big.mark = ","), digits = 0) |>
    kable_styling(full_width = FALSE, position = "center",
                  latex_options = c("striped", "hold_position"))
```

### c. Spending by SubCategory For This Month

```{r, fig.width=13, fig.height=20}

a <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Health & Wellness") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Health & Wellness", labelColor = EH_LabelColor)

b <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Home") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Home", labelColor = EH_LabelColor)

c <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Travel") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel", labelColor = EH_LabelColor)

d <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Groceries") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Groceries", labelColor = EH_LabelColor)

e <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Travel Local") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel Local", labelColor = EH_LabelColor)

f <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |> dplyr::filter(ToDelete == 0, Category=="Shopping") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Shopping", labelColor = EH_LabelColor)

g <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Food & Drink") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Food & Drink", labelColor = EH_LabelColor)

h <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Gifts & Donations") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Gifts & Donations", labelColor = EH_LabelColor)

i <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Car") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Car", labelColor = EH_LabelColor)

j <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Entertainment") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Entertainment", labelColor = EH_LabelColor)

k <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Education") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Education", labelColor = EH_LabelColor)

l <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Subscriptions") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "SubScriptions", labelColor = EH_LabelColor)


grid.arrange(a, b, c, d, e, f, g, h, i, j, k, l, ncol=3)
```

### d. Spending by SubCategory YTD

```{r, fig.width=13, fig.height=20}

a <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Health & Wellness") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Health & Wellness, YTD", labelColor = EH_LabelColor)

b <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Home") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Home, YTD", labelColor = EH_LabelColor)

c <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Travel") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel, YTD", labelColor = EH_LabelColor)

d <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Groceries") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Groceries, YTD", labelColor = EH_LabelColor)

e <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Travel Local") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel Local, YTD", labelColor = EH_LabelColor)

f <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Shopping")|> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Shopping, YTD", labelColor = EH_LabelColor)

g <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Food & Drink") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Food & Drink, YTD", labelColor = EH_LabelColor)

h <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Gifts & Donations") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Gifts & Donations, YTD", labelColor = EH_LabelColor)

i <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Car") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Car, YTD", labelColor = EH_LabelColor)

j <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Entertainment") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Entertainment, YTD", labelColor = EH_LabelColor)

k <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Education") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Education, YTD", labelColor = EH_LabelColor)

l <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Subscriptions") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "SubScriptions, YTD", labelColor = EH_LabelColor)


grid.arrange(a, b, c, d, e, f, g, h, i, j, k, l, ncol=3)
```



## 2. Categories in Detail

### a. Home

```{r fig.width=10, fig.height = 3}

xCategory="Home"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### b. Shopping

```{r fig.width=10, fig.height = 3}

xCategory="Shopping"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

#### 1. With Amazon Info Coming From Website

```{r fig.width = 14, fig.height=8}

xCategory="Shopping"
dfExSum <- EHFinances_FilterByCategory(dfExpensesReviewed, "Shopping")

a <- paste0("Total shopping from bank info: ", sum(dfExSum$Amount))
b <- paste0("Total shopping from Amazon: ", sum(dfShopping$Amount))

a
b

z <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfShopping |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = paste0(xCategory, ", ", Folder))

q <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfShopping_YTD |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = paste0(xCategory, ", YTD"))

grid.arrange(z,q,ncol=2)

EHFinances_CreateTopSpendingTable(dfShopping, xCategory, Folder, fontSize=8)
EHFinances_CreateTopSpendingTable(dfShopping_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

a <- dfShopping |>
  group_by(xScale) |>
  dplyr::summarize(Count = n(), Expenditures = sum(Amount)) |>
kable(
    col.names = c("xScale", "Count", "Expenditures"),
    caption = paste0("Count and Amount by Scale, ", Folder),
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8)
a


```

### c. Car

```{r fig.width=10, fig.height = 3}

xCategory="Car"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### d. Health and Wellness

```{r fig.width=10, fig.height = 3}

xCategory="Health & Wellness"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### e. Food and Drink

```{r fig.width=10, fig.height = 3}

xCategory="Food & Drink"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

a <- dfExpensesReviewed |>
  dplyr::filter(Category=="Food & Drink") |>
  group_by(SubCategory) |>
  dplyr::summarize(Count = n()) |>
kable(
    col.names = c("Type", "Count"),
    caption = paste0("Count by Type, ", Folder),
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8
  )

b <- dfExpensesReviewed_YTD |>
  dplyr::filter(Category=="Food & Drink") |>
  group_by(SubCategory) |>
  dplyr::summarize(Count = n()) |>
kable(
    col.names = c("Type", "Count"),
    caption = "Count by Type, YTD",
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8
  )

kables(list(a, b), format = "pdf") %>%
  kable_styling(position = "center")

```
### f. Entertainment

```{r fig.width=10, fig.height = 3}

xCategory="Entertainment"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### g. Groceries

```{r fig.width=10, fig.height = 3}

xCategory="Groceries"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### h. Subscriptions

```{r fig.width=10, fig.height = 3}

xCategory="Subscriptions"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### i. Gifts and Donations

```{r fig.width=10, fig.height = 3}

xCategory="Gifts & Donations"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### j. Travel

```{r fig.width=10, fig.height = 3}

xCategory="Travel"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### k. Travel Local

```{r fig.width=10, fig.height = 3}

xCategory="Travel Local"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```


```{r}

  dfCat <- dfExpensesReviewed |>
    dplyr::filter(SubCategory=="Utilities")


x <- EHFinances_FilterByCategory(dfExpensesReviewed, "Education")

```

## 3. Payment Tracking

```{r}

kable(dfExpensesReviewed |> dplyr::filter(PaidMonthly==1) |>
  dplyr::mutate(Description = substr(Description, 1, 45)) |> dplyr::arrange(Description) |> dplyr::select(-PaidMonthly, -SupercedesTrip, -Memo, -ToDelete, -Type, -ID, -Corrected),  caption = "Actual Payments", format.args = list(big.mark = ","), digits = 0) |>
    kable_styling(full_width = FALSE, position = "center",
                  latex_options = c("striped", "hold_position"))

kable(dfCategories |> dplyr::filter(PaidMonthly==1) |> dplyr::arrange(xKey) |> dplyr::select(-PaidMonthly, -SupercedesTrip),  caption = "Accounts To Be Paid Monthly", format.args = list(big.mark = ","), digits = 0) |>
    kable_styling(full_width = FALSE, position = "center",
                  latex_options = c("striped", "hold_position"))

```

