---
title: "Jenny and Eric Spending Report, June"
output:
  pdf_document:
    toc: true
    toc_depth: 5
date: "2026-06-01"
---

```{r setup, include = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning =  FALSE, message = FALSE)
```

```{r}
library(XML)
library(RCurl)
library(rlist)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(readr)
library(sf)
unloadNamespace("EHData")
devtools::install_github("ericonsi/EHData")
library(EHData)
library(devtools)
library(roxygen2)
library(Hmisc)
library(psych)
library(tidyverse)
library(skimr)
library(purrr)
library(tidyr)
library(tidyverse)
library(gridExtra)
library(lubridate)
library(fastDummies)
library(data.table)
library(mltools)
library(MASS)
library(car)
library(patchwork)
library(ggthemes)
library(tinytex)
library(stats)
library(ggsci)
library(scales)
library(naniar)
library(caret)
library(pROC)
library(methods) 
library(sf)
library(mapproj)
library(maps)
#library(rnaturalearth)
library(rnaturalearthdata)
library(usmap)
library(tsibbledata)
library(tsibble)
library(forecast)
library(fpp3)
library(fable)
library(lme4)
library(rvest)
library(factoextra)
library(gridGraphics)
library(kableExtra)
library(anytime)
unloadNamespace("EHDataFinances")
devtools::install_github("ericonsi/EHDataFinances")
library(EHDataFinances)
library(knitr)
library(datefixR)
```

```{r}
#Assign Month

xMonth="2606"
Folder = xMonth
EH_Turquoise = "#33a0a0"
EH_Cream = "#FFFEE0"
EH_Squash = "#c95b0c"
EH_LabelColor = "#5d3f6a"

```

```{r}

# Import data
dfExpenses <- EHFinances_ImportRawAccountFiles(xMonth)[[1]]
dfCategories <- EHFinances_ImportCategories()
dfAmazonOrders <- EHFinances_ImportAmazonOrders(xMonth)
dfExpenses2025 <- EHFinances_Import2025()

```

```{r}
# Assign Categories and Shocks

dfExpenses2 <- EHFinances_AssignCategoriesAndSubcategories(dfExpenses)
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2025-12-28", "2026-01-08", "Rio")
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2026-02-2", "2026-02-10", "Puerto Rico")
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2026-04-24", "2026-04-26", "Atlanta")
dfExpenses3 <- EHFinances_AssignTrips(dfExpenses2, "2026-06-13", "2026-06-14", "Maine")
dfExpenses4 <- EHFinances_AssignRuby(dfExpenses3)
dfExpenses5 <- EHFinances_AssignAccountsToDelete(dfExpenses4)
dfExpenses6 <- EHFinances_ApplyBusinessRules(dfExpenses5)
dfExpenses7 <- EHFinances_AssignFoodSubCategories(dfExpenses6)
dfExpenses8 <- EHFinances_AssignShoppingCategories(dfExpenses7)

```

```{r}

#Write or open override file

dfExpenses9 <- EHFinances_WriteOrOpenOverrideFile(dfExpenses8, Folder=xMonth, AlreadyWritten = FALSE)

```

```{r}
# Disaggregate Files - only works after override file has been written

liExpenseDFs <- EHFinances_CreateShockAndExpenseDFs(dfExpenses9)

dfExpensesReviewed = liExpenseDFs[[1]]
dfRuby <- liExpenseDFs[[2]]
dfRenovation <- liExpenseDFs[[3]]
dfIncomeTaxes <- liExpenseDFs[[4]]

```

```{r}

dfShopping <- EHFinances_WriteOrOpenShoppingFile(dfExpensesReviewed, Folder=xMonth, AlreadyWritten = FALSE)

```

```{r}
# Create ytd dfs
# Needs an Override_r file or there will be "Error in liExpenseDFs[[1]][[2]] : subscript out of bounds"


liExpenseDFs <- EHFinances_CreateYtdDfs(Folder)

dfExpensesReviewed_YTD = liExpenseDFs[[1]][[1]]
dfRuby_YTD <- liExpenseDFs[[1]][[2]]
dfRenovation_YTD <- liExpenseDFs[[1]][[3]]
dfIncomeTaxes_YTD <- liExpenseDFs[[1]][[4]]
dfShopping_YTD <- liExpenseDFs[[2]][[1]]
 

```

```{r}
#Perform Budget Analysis

dfBudgetTargets <- read_csv(paste0("D:\\RStudio\\Finances\\AnnualBudgetTargets.csv"), na = c("")) 
v <- setdiff(as.vector(dfExpensesReviewed$Category), as.vector(dfBudgetTargets$Category))

if(length(v != 0)){
  print(paste("Differences that need to be reconciled to clear this error: ", v))
}

liBudget <- EHFinances_CreateBudgetAnalysisDFs(dfExpensesReviewed, dfExpensesReviewed_YTD, Folder)

dfBudget <- liBudget[[1]]
dfBudget_YTD <- liBudget[[2]]
dfBudget_AnnualTargets <- dfBudget |>
  mutate(Amount_Budget=Amount_Budget*12) |>
  dplyr::select(Category, Amount_Budget) |>
  dplyr::rename(Amount=Amount_Budget)

```

## 1. Overall Spending

```{r fig.width = 14, fig.height=8}

EHFinances_CreateTotalsTable(dfExpensesReviewed, dfExpensesReviewed_YTD, dfRuby, dfRuby_YTD, dfRenovation, dfRenovation_YTD, dfIncomeTaxes, dfIncomeTaxes_YTD, dfBudget, dfBudget_YTD, Folder)

```

### a. Spending by Category

```{r fig.width = 14, fig.height=8}

a <- EHData::EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |> dplyr::select(Category, Amount), xfill =EH_Turquoise, rectfill = EH_Cream, font_size = 15, xtitle = "Total Spent by Category, 2602", labelColor=EH_LabelColor, labelSize = 5)

b <- EHData::EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |> dplyr::select(Category, Amount), xfill =EH_Turquoise, rectfill = EH_Cream, font_size = 15, xtitle = "Total Spent by Category, YTD", labelColor=EH_LabelColor, labelSize = 5)

par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
grid.arrange(a, b, ncol = 2)

```

### b. Spending Compared to Budget (Goal: $173,000/Year, $14,417 per month)

```{r}
#par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
grid.arrange(liBudget[[3]], liBudget[[4]], ncol = 2)

Total <- c("TOTAL", sum(dfBudget$Amount_Budget), sum(dfBudget$Amount_Spent), sum(dfBudget$Differential))
           
dfBudgetWithTotal <- rbind(dfBudget, Total)


Total_YTD <- c("TOTAL", sum(dfBudget_YTD$Amount_Budget), sum(dfBudget_YTD$Amount_Spent), sum(dfBudget_YTD$Differential))
           
dfBudgetWithTotal_YTD <- rbind(dfBudget_YTD, Total_YTD)

EHFinances_MakeKableTable(dfBudgetWithTotal,  "Budget Summary")
EHFinances_MakeKableTable(dfBudgetWithTotal_YTD,  "Budget Summary YTD")

```

### c. Spending by SubCategory For This Month

```{r, fig.width=13, fig.height=20}

a <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Health & Wellness") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Health & Wellness", labelColor = EH_LabelColor)

b <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Home") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Home", labelColor = EH_LabelColor)

c <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Travel") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel", labelColor = EH_LabelColor)

d <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Groceries") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Groceries", labelColor = EH_LabelColor)

e <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Travel Local") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel Local", labelColor = EH_LabelColor)

f <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |> dplyr::filter(ToDelete == 0, Category=="Shopping") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Shopping", labelColor = EH_LabelColor)

g <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Food & Drink") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Food & Drink", labelColor = EH_LabelColor)

h <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Gifts & Donations") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Gifts & Donations", labelColor = EH_LabelColor)

i <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Car") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Car", labelColor = EH_LabelColor)

j <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Entertainment") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Entertainment", labelColor = EH_LabelColor)

k <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Education") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Education", labelColor = EH_LabelColor)

l <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed |>  dplyr::filter(ToDelete == 0, Category=="Subscriptions") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "SubScriptions", labelColor = EH_LabelColor)


grid.arrange(a, b, c, d, e, f, g, h, i, j, k, l, ncol=3)
```

### d. Spending by SubCategory YTD

```{r, fig.width=13, fig.height=20}

a <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Health & Wellness") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Health & Wellness, YTD", labelColor = EH_LabelColor)

b <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Home") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Home, YTD", labelColor = EH_LabelColor)

c <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Travel") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel, YTD", labelColor = EH_LabelColor)

d <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Groceries") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Groceries, YTD", labelColor = EH_LabelColor)

e <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Travel Local") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Travel Local, YTD", labelColor = EH_LabelColor)

f <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Shopping")|> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Shopping, YTD", labelColor = EH_LabelColor)

g <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Food & Drink") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Food & Drink, YTD", labelColor = EH_LabelColor)

h <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Gifts & Donations") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Gifts & Donations, YTD", labelColor = EH_LabelColor)

i <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Car") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Car, YTD", labelColor = EH_LabelColor)

j <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Entertainment") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Entertainment, YTD", labelColor = EH_LabelColor)

k <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Education") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "Education, YTD", labelColor = EH_LabelColor)

l <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfExpensesReviewed_YTD |>  dplyr::filter(ToDelete == 0, Category=="Subscriptions") |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = "SubScriptions, YTD", labelColor = EH_LabelColor)


grid.arrange(a, b, c, d, e, f, g, h, i, j, k, l, ncol=3)
```

### e. Renovation Breakdown YTD

```{r}

dfRenovationsYTD_Grouped <- dfRenovation_YTD |>
  group_by(SubCategory) |>
  dplyr::summarise(Total = sum(Amount)) 

dfxx <- bind_rows(dfRenovationsYTD_Grouped, tibble(SubCategory = "TOTAL", Total = sum(dfRenovationsYTD_Grouped$Total)))

EHFinances_MakeKableTable(dfxx, "Renovation Breakdown YTD")

```



## 2. Categories in Detail

### a. Home

```{r fig.width=10, fig.height = 3}

xCategory="Home"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### b. Shopping

```{r fig.width=11, fig.height = 3}

xCategory="Shopping"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

#### With Amazon Info Coming From Website

```{r fig.width = 14, fig.height=8}

xCategory="Shopping"
dfExSum <- EHFinances_FilterByCategory(dfExpensesReviewed, "Shopping")

a3 <- sum(dfExSum$Amount)
b3 <- sum(dfShopping$Amount)
df3 <- data.frame("Info_Source:" = 1:2, "TOTAL:" = 1:2)
df3[[1,1]] = "Banks"
df3[1,2] = a3
df3[[2,1]] = "Amazon"
df3[2,2] = b3

kable(df3)

z <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfShopping |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = paste0(xCategory, ", ", Folder))

q <- EHSummarize_CategoryByTotal_ReturnsSingleTable(dfShopping_YTD |> dplyr::select(SubCategory, Amount), xfill =EH_Squash, rectfill = EH_Cream, font_size = 9, xtitle = paste0(xCategory, ", YTD"))

grid.arrange(z,q,ncol=2)

EHFinances_CreateTopSpendingTable(dfShopping, xCategory, Folder, fontSize=8)
EHFinances_CreateTopSpendingTable(dfShopping_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

a <- dfShopping |>
  group_by(xScale) |>
  dplyr::summarize(Count = n(), Expenditures = sum(Amount)) |>
kable(
    col.names = c("xScale", "Count", "Expenditures"),
    caption = paste0("Count and Amount by Scale, ", Folder),
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8)
a


```

### c. Car

```{r fig.width=10, fig.height = 3}

xCategory="Car"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

```{r}


dfExpenses2025Gas <- dfExpenses2025 |> 
  dplyr::filter(SubCategory=="Gas")  |>
  dplyr::group_by(month(`Transaction Date`)) |>
  dplyr::summarise(Expenditures = sum(Amount)) |> 
  dplyr::rename(Month = 1)
  
dfExpenses2025Maintenance <- dfExpenses2025 |> 
  dplyr::filter(SubCategory=="Maintenance")  |>
  dplyr::group_by(month(`Transaction Date`)) |>
  dplyr::summarise(Expenditures = sum(Amount)) |> 
  dplyr::rename(Month = 1)


  a <- ggplot(dfExpenses2025Gas, aes(x = Month)) +
    geom_line(aes(y = Expenditures, color = "Expenditures"), size = 1) +
    geom_point(aes(y = Expenditures, color = EH_LabelColor), size = 3) +
    theme(panel.background = element_rect(fill = EH_Cream, colour = "black"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual("", values = c("Expenditures" = EH_Turquoise)) +
    scale_x_continuous(breaks = function(x) seq(ceiling(min(x)), floor(max(x)), by = 1)) +
    ggtitle("Gas per Month, 2025") +
    scale_y_continuous(limits = c(0, NA)) +
    theme(legend.position="none")

    b <- ggplot(dfExpenses2025Maintenance, aes(x = Month)) +
    geom_line(aes(y = Expenditures, color = "Expenditures"), size = 1) +
    geom_point(aes(y = Expenditures, color = EH_LabelColor), size = 3) +
    theme(panel.background = element_rect(fill = EH_Cream, colour = "black"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    scale_color_manual("", values = c("Expenditures" = EH_Turquoise)) +
    scale_x_continuous(breaks = function(x) seq(ceiling(min(x)), floor(max(x)), by = 1)) +
    ggtitle("Maintenance per Month, 2025") +
    scale_y_continuous(limits = c(0, NA)) +
    theme(legend.position="none")


grid.arrange(a,b, ncol=2)


  
```


### d. Health and Wellness

```{r fig.width=10, fig.height = 3}

xCategory="Health & Wellness"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### e. Food and Drink

```{r fig.width=10, fig.height = 3}

xCategory="Food & Drink"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

a <- dfExpensesReviewed |>
  dplyr::filter(Category=="Food & Drink") |>
  group_by(SubCategory) |>
  dplyr::summarize(Count = n()) |>
kable(
    col.names = c("Type", "Count"),
    caption = paste0("Count by Type, ", Folder),
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8
  )

b <- dfExpensesReviewed_YTD |>
  dplyr::filter(Category=="Food & Drink") |>
  group_by(SubCategory) |>
  dplyr::summarize(Count = n()) |>
kable(
    col.names = c("Type", "Count"),
    caption = "Count by Type, YTD",
    align = c("l", "r")
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE,
    font_size=8
  )

kables(list(a, b), format = "pdf") %>%
  kable_styling(position = "center")

```
### f. Entertainment

```{r fig.width=10, fig.height = 3}

xCategory="Entertainment"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### g. Groceries

```{r fig.width=10, fig.height = 3}

xCategory="Groceries"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### h. Subscriptions

```{r fig.width=10, fig.height = 3}

xCategory="Subscriptions"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### i. Gifts and Donations

```{r fig.width=10, fig.height = 3}

xCategory="Gifts & Donations"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### j. Travel

```{r fig.width=10, fig.height = 3}

xCategory="Travel"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```

### k. Travel Local

```{r fig.width=10, fig.height = 3}

xCategory="Travel Local"
EHFinances_CategoryDetails(dfExpensesReviewed, dfExpensesReviewed_YTD, xCategory=xCategory, dfBudget, Folder)
EHFinances_CreateTopSpendingTable(dfExpensesReviewed_YTD, xCategory = xCategory, Folder, fontSize=8, ytd=TRUE)

```


```{r}

  dfCat <- dfExpensesReviewed |>
    dplyr::filter(SubCategory=="Utilities")


x <- EHFinances_FilterByCategory(dfExpensesReviewed, "Education")

```

## 3. Monthly Payment Tracking

```{r}

EHFinances_MakeKableTable(dfExpensesReviewed |> dplyr::filter(PaidMonthly==1) |>
  dplyr::mutate(Description = substr(Description, 1, 30)) |> dplyr::arrange(Description) |> dplyr::select(-PaidMonthly, -SupercedesTrip, -Memo, -ToDelete, -Type, -ID, -Corrected),  "Actual Payments")

EHFinances_MakeKableTable(dfCategories |> dplyr::filter(PaidMonthly==1) |> dplyr::arrange(xKey) |> dplyr::select(-PaidMonthly, -SupercedesTrip),  "Accounts To Be Paid Monthly")

```


## 4. Top 100 Expenses

```{r}

EHFinances_CreateTopSpendingTable_AllYTD(dfExpensesReviewed_YTD, 100, Folder, fontSize=8, ytd=TRUE)

```

## 5. Estimated Expenses

### A. Estimated Core Expenses

```{r}



```


```{r}

dfExpenses2025Totals <- dfExpenses2025 |>
  group_by(Category, SubCategory)  |>
  dplyr::summarise(TOTAL=sum(Amount))

#write_csv(dfExpenses2025Totals, paste0("D:\\RStudio\\Finances\\dfExpenses2025Totalsp.csv"))

dfExpenses2025Totalsr <- read_csv(paste0("D:\\RStudio\\Finances\\dfExpenses2025Totalsr.csv"))
  
dfExpenses2025Totalsr_WithTotal <- dfExpenses2025Totalsr |> 
dplyr::filter(Core==1) |>
group_by(Category) |> 
dplyr::summarise(Estimated = sum(Estimated)) |>
dplyr::select(Category, Estimated) |>
  dplyr::arrange(Category)

Total = c("TOTAL", sum(dfExpenses2025Totalsr$Estimated))
dfExpenses2025Totalsr_WithTotal <- rbind(dfExpenses2025Totalsr_WithTotal, Total) |>
  mutate(Estimated=as.numeric(Estimated))

EHFinances_MakeKableTable(dfExpenses2025Totalsr_WithTotal,  "Estimated Annual Expense")  

EHFinances_MakeKableTable(dfExpenses2025Totalsr |> dplyr::filter(Core==1) |> dplyr::arrange(Category, SubCategory) |>  dplyr::select(Category, SubCategory, Estimated),  "Estimated Annual Expenses Breakdown")

```

### B. Projected Savings with a 20% Reduction Per Category Based on Current Budget

```{r}

dfBudget_AnnualTargets_Savings <- dfBudget_AnnualTargets |>
  mutate(`Projected Savings` = .2*Amount) |>
  mutate(`Projected Savings` = round(`Projected Savings`, 0)) |>
  dplyr::arrange(desc(`Projected Savings`)) |>
  dplyr::rename(`Current Budget Target` = Amount)

Total = c("Total", sum(dfBudget_AnnualTargets_Savings$`Current Budget Target`), sum(dfBudget_AnnualTargets_Savings$`Projected Savings`)) 

dfBudget_AnnualTargets_Savings <- rbind(dfBudget_AnnualTargets_Savings, Total) |>
  mutate(`Projected Savings` = as.numeric(`Projected Savings`), `Current Budget Target` = as.numeric(`Current Budget Target`))

EHFinances_MakeKableTable(dfBudget_AnnualTargets_Savings, "Estimated Savings")
  
```


